Reconstructing Propositional Proofs in Type Theory

### 2017-10-25 paper/sections/proof-reconstruction/clausify.tex
more fixes.
strip equations.

The \clausify rule transforms a
propositional formula into its clausal normal form, a conjunction
of clauses. A \emph{clause} is the disjunction of zero or more
literals and a \emph{literal} is an atom (positive literal) or a
negation of an atom (negative literal).
It is important to notice that this kind of conversion between one formula
to its clausal normal form is not unique, and \Metis has a customized
approach to perform that transformation. That is the reason we perform some
reordering for the \CNF of the source formula to fulfill this issue.

@@

\begin{verbatim}
fof(a1, axiom, p => (q & r)).
...
fof(norm0, ~ p | (q & r), inf(canonicalize, [a1])).
fof(norm1, (~ p | q) & (~ p | r), inf(clausify, [norm0])).
...
\end{verbatim}

@@

\begin{proof}
If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma. Otherwise, we use Theorem~\ref{lem:reorder-and-or} and Theorem~\ref{lem:cnf}.
\end{proof}

>>>>

The \clausify rule transforms a
propositional formula into its clausal normal form, a conjunction
of clauses. A \emph{clause} is the disjunction of zero or more
literals.
It is important to notice that this kind of conversion between one formula
to its clausal normal form is not unique, and \Metis has a customized
approach to perform that transformation. That is the reason we perform some
reordering for the \CNF of the source formula to fulfill this issue.

@@

\begin{verbatim}
fof(a1, axiom, p ⇒ (q ∧ r)).
...
fof(norm0, ¬ p ∨ (q ∧ r), inf(canonicalize, [a1])).
fof(norm1, (¬ p ∨ q) ∧ (¬ p ∨ r), inf(clausify, [norm0])).
...
\end{verbatim}

@@

\begin{proof}
If $φ ≡ ψ$, $Γ ⊢ \fclausify~φ~ψ$ normalizes to $Γ ⊢ ψ$. The conclusion follows by applying the $\fsubst$ lemma. Otherwise, we use Lemma~\ref{lem:reorder-and-or} and Lemma~\ref{lem:cnf}.
\end{proof}
